Analysis of Bauer et al. (unpublished) Field experiment: <br> Favourable Conservation Status (FCS)

### 2022-12-06 R/model_fcs_check.Rmd

```{r collapse = TRUE, message = FALSE}
load(file = here("outputs", "models", "model_fcs_2.Rdata"))
load(file = here("outputs", "models", "model_fcs_2_test.Rdata"))
#load(file = here("outputs", "models", "model_fcs_full.Rdata"))
m_1 <- m2
m_2 <- m2_test
#m_2 <- m_full
```

@@

Just, to get exact values if necessary, which is not possible from the figure

```{r max_height = "1000px"}
(emm <- emmeans(m_1, revpairwise ~ target_type + sand_ratio |
                  exposition | survey_year_fct, type = "response"))
```

@@

```{r echo = FALSE, max_height = "500px"}
sessionInfo()
```

>>>>

```{r collapse = TRUE, message = FALSE}
load(file = here("outputs", "models", "model_fcs_2.Rdata"))
load(file = here("outputs", "models", "model_fcs_full.Rdata"))
m_1 <- m2
m_2 <- m_full
```

@@

Effect sizes are presented just to get exact values of the means if necessary.

```{r}
(emm <- emmeans(m_1, revpairwise ~ target_type + sand_ratio |
                  exposition | survey_year_fct, type = "response"))
```

@@

```{r echo = FALSE}
sessionInfo()
```
